Logarithmic Space Verifiers on NP-complete

### 2019-11-12 doc/manuscript.tex
Updated the content proof

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. Consequently, this is a result of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}

@@

On the one hand, every language in $L_{1} \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

On the other hand, every language in $L_{2} \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

>>>>

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. We can extend this result when $T(n)$ is not a constant \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}

@@

On the one hand, every language in $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.
